---
title: "Graphical Summary for Fluoxetine"
author: "Zachary Rowson"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gabi)
library(data.table)
library(ggplot2)
library(tcplfit2)
```

## Introduction

This document will graphically summarize gabi analysis results for Fluoxetine and display graphics that summarize results for the DNT60 set.

```{r}
# declare chemical name and index
chemical <- "Fluoxetine"
i <- which(chms == "Fluoxetine")

# gather experimental group number for Fluoxetine
group <- unique(gabi::data_egids(pmr0)[cpid==chemical, egid])

# isolate relevant rows
rows <- lapply(rows_n, `[[`, i)
```

## Graphics specific to Individual Chemicals

### Time Series Visualizations

```{r}
gabi::plot_tSeries(pmr0, chemical = chemical, prsp = "SS")
gabi::plot_tSeries(pmr0, chemical = chemical, prsp = "PA")
```

### Endpoint Distributions: Before and After Transform

```{r}
lapply(mc0, function(data) {
  gabi::plot_eDist(data, chemical = chemical)
})

lapply(mc0_n, function(endp) {
  data <- endp[[1]]
  gabi::plot_eDist(data, chemical = chemical)
})
```

### Benchmark Concentration Analyses

```{r}
fits <- lapply(rows, gabi::concRespCoreZR, do.plot = TRUE)
lapply(fits, `[[`, "plot")
```

## Study-Level Summarizing Graphics

### Heatmaps: Hitcalls and BMDs

```{r}
pheatmap::pheatmap(hits, 
                   main = "Hitcall Heatmap for DNT60 Chemicals",
                   cluster_rows = T, cluster_cols = F,
                   cutree_rows = 6,
                   color = viridis::viridis(9),
                   annotation_col = ann.df, annotation_colors = list(Phase=ann_colors))
```
