---
title: "Graphical Summary for Fluoxetine"
author: "Zachary Rowson"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gabi)
library(data.table)
library(ggplot2)
library(tcplfit2)
library(pheatmap)
```

## Introduction

This document will graphically summarize gabi analysis results for Fluoxetine and display graphics that summarize results for the DNT60 set.

```{r}
# declare chemical name and index
chemical <- "Fluoxetine"
i <- which(chms == "Fluoxetine")

# gather experimental group number for Fluoxetine
group <- unique(gabi::data_egids(pmr0)[cpid==chemical, egid])

# isolate relevant rows
rows <- lapply(rows_n, `[[`, i)
```

## Graphics specific to Individual Chemicals

### Time Series Visualizations

```{r}
gabi::plot_tSeries(pmr0, chemical = chemical, prsp = "SS")
gabi::plot_tSeries(pmr0, chemical = chemical, prsp = "PA")
```

### Endpoint Distributions: Before and After Transform

```{r}
lapply(mc0, function(data) {
  gabi::plot_eDist(data, chemical = chemical)
})

lapply(mc0_n, function(endp) {
  data <- endp[[1]]
  gabi::plot_eDist(data, chemical = chemical)
})
```

### Benchmark Concentration Analyses

```{r}
fits <- lapply(rows, gabi::concRespCoreZR, do.plot = TRUE)
lapply(fits, `[[`, "plot")
```

## Study-Level Summarizing Graphics

### Heatmaps: Hitcalls and BMDs

```{r}
pheatmap::pheatmap(hits, 
                   main = "Hitcall Heatmap for DNT60 Chemicals",
                   cluster_rows = T, cluster_cols = F,
                   cutree_rows = 6,
                   color = viridis::viridis(9),
                   annotation_col = ann.df, annotation_colors = list(Phase=ann_colors))

pheatmap::pheatmap(to_fit, 
                   main = "BMD Heatmap for DNT60 Chemicals",
                   cluster_rows = F, cluster_cols = F,
                   cutree_rows = 6,
                   color = viridis::viridis(9),
                   annotation_col = ann.df, annotation_colors = list(Phase=ann_colors))
```

### Venn/Euler Diagrams
```{r, echo = FALSE}
library(VennDiagram)
library(grid)
library(gridExtra)

# use habituation endpoints as a practice round

## look at overlap of hits in hbt_L and hbt_D
sets <- VennDiagram::calculate.overlap(e.grps[c("hbt_L", "hbt_D")])

## calculate set sizes
set.size <- lapply(sets, length)

## create venn diagrams / Euler graphics
venn <- draw.pairwise.venn(set.size[[1]], set.size[[2]], set.size[[3]],
                   category = c("hbt_L", "hbt_D"),
                   euler.d = TRUE, scaled = TRUE,
                   cat.cex = rep(1.5,2),
                   fill = viridis::viridis(2),
                   alpha = rep(0.5,2),
                   ind = FALSE)
# venn.grob <- gTree(children = venn)
grid.arrange(gTree(children = venn),
             top = textGrob("Habituation in Light and Dark Overlap", gp=gpar(fontsize=24)))
rm(sets, set.size, venn)


# look at overlap of endpoint activity in Light and Dark exclude AUC and avgJ

## look at overlap of hits in Light
sets <- VennDiagram::calculate.overlap(e.grps[c("avgS_L","avgA_L","hbt_L")])
venn <- VennDiagram::venn.diagram(e.grps[c("avgS_L","avgA_L","hbt_L")],
                          filename = NULL,
                          main = "Light Endpoints Overlap", main.cex = 2,
                          fill = viridis::viridis(3),
                          euler.d = TRUE, scaled = TRUE)
grid.arrange(gTree(children = venn))
## calculate set sizes
set.size <- lapply(sets, length)

## look at overlap of hits in Dark
sets <- VennDiagram::calculate.overlap(e.grps[c("avgS_D","avgA_D","hbt_D")])
venn <- VennDiagram::venn.diagram(e.grps[c("avgS_D","avgA_D","hbt_D")],
                                  filename = NULL,
                                  main = "Dark Endpoints Overlap", main.cex = 2,
                                  fill = viridis::viridis(3),
                                  euler.d = TRUE, scaled = TRUE)
grid.arrange(gTree(children = venn))

## look at overlap of Transitory hits
sets <- VennDiagram::calculate.overlap(e.grps[c("strtlA","strtlAavg","strtlF")])
venn <- VennDiagram::venn.diagram(e.grps[c("strtlA","strtlAavg","strtlF")],
                                  filename = NULL,
                                  main = "Transitory Endpoints Overlap", main.cex = 2,
                                  fill = viridis::viridis(3),
                                  euler.d = TRUE, scaled = TRUE)
grid.arrange(gTree(children = venn))

## look at overlap of avgS_L and strtlAavg hits
sets <- VennDiagram::calculate.overlap(e.grps[c("strtlAavg","avgS_L")])
venn <- VennDiagram::venn.diagram(e.grps[c("strtlAavg","avgS_L")],
                                  filename = NULL,
                                  main = "avgS_L and srtlAavg Overlap", main.cex = 2,
                                  fill = viridis::viridis(2),
                                  euler.d = TRUE, scaled = TRUE)
grid.arrange(gTree(children = venn))

## look at overlap of Light, Dark, and Transitory activity
lapply(c("Light","Transitory","Dark"), function(prd) hit.p.prfls[])
p.grps <- list(Light = hit.p.prfls[Light==1, cpid],
               Dark = hit.p.prfls[Dark==1, cpid],
               Transition = hit.p.prfls[Startle==1, cpid])

sets <- VennDiagram::calculate.overlap(p.grps)
venn <- VennDiagram::venn.diagram(p.grps,
                                  filename = NULL,
                                  main = "Activity by Period Overlap", main.cex = 2,
                                  fill = viridis::viridis(3),
                                  euler.d = TRUE, scaled = TRUE)
grid.arrange(gTree(children = venn))
```
